Analysis of competitive surfing tournaments with generalized Bradley-Terry likelihoods

### 2022-09-27 inst/jss_4382.tex
fixes #158

>>>>

\textcolor{blue}{Response: Function {\tt maxp()} can return many
  additional objects in addition to the evaluate; standard idiom is to
  pass argument {\tt give = TRUE}.  In particular, a list with
  elements
  \begin{itemize}
  \item {\tt \$hessian} the Hessian matrix: passing argument {\tt give
    = TRUE, hessian = TRUE} returns the Hessian matrix.  However, this
    is restricted to {\tt hyper2} objects and I would add that {\tt
      hyper3} objects are much, much, harder to differentiate than
    {\tt hyper2} objects (let alone second derivatives).
    \item {\tt \$likes} likelihoods
    \item {\tt \$par} the evaluate
  \end{itemize}
  The package includes summary methods and print method for summary
  objects.\\ Some of the suggestions are good for regression-type
  analysis, but do not really carry over to the current
  likelihood-based approach.  The {\tt hyper2} package is predicated
  on straightforward idiom to create and manipulate likelihood
  functions; statistical tests are (to me) just one application of
  likelihood functions.}
